Visualize ukb whole genome, using ctwas results

### 2021-07-31 analysis/simulation-ctwas-ukbWG-gtex.adipose_visual.Rmd
simulation paper figures

```{r output dir}
outputdir <- "~/causalTWAS/simulations/simulation_ctwas_rss_20210117/"

source("~/causalTWAS/causal-TWAS/analysis/summarize_ctwas_plots.R")
source("~/causalTWAS/causal-TWAS/analysis/visual_twas_plots.R")
```

```{r functions file}

@@

  a <- merge(a, b, by = "name")
  a$ifcausal <- ifelse(a$name %in% cau, "Causal", "Non causal" )

  if (thin !=1){
    b <- a[a$type == "gene" | (a$type == "SNP" & a$ifcausal == "Causal") | 
             (a$type == "SNP" & a$ifcausal == "Non causal" & rbinom(nrow(a), 1, thin) ==1)]
  }

@@

  colnames(a)[colnames(a) == "susie_pip"] <-  "susiePIP"
  colnames(a)[colnames(a) == "pos"] <-  "p0"

@@

## Simulation

First three rows are for genes, last three rows are for SNPs.

```{r sim 2, out.width = "98%", out.height="95%"}
chrom <- 7
runtag <- "ukb-s80.45-adi"
simutag <- "2-1"
configtag <- 1

susief <- paste0(outputdir, runtag, "_simu", simutag, "_config", configtag, ".susieIrss.txt")
pf <- paste0(outputdir, runtag, "_simu",simutag)
phenof <- paste0(outputdir, runtag, "_simu", simutag, "-pheno.Rd")
plot_all(susief, pf, phenof, chrom, thin = 0.01)
```

>>>>

```{r functions file}
source("~/causalTWAS/causal-TWAS/analysis/summarize_ctwas_plots.R")
source("~/causalTWAS/causal-TWAS/analysis/visual_twas_plots.R")

@@

  a <- merge(a, b, by = "name", all = T)
  a$ifcausal <- ifelse(a$name %in% cau, "Causal", "Non causal" )
  a[is.na(a$type),"type"] <- "SNP"

  if (thin !=1){
    a <- a[ !is.na(a$type) | a$ifcausal == "Causal" | 
             (a$ifcausal == "Non causal" & rbinom(nrow(a), 1, thin) ==1)]
  }

@@

  colnames(a)[colnames(a) == "susie_pip"] <-  "susiePIP"

@@

## Scatter plot

```{r sim 2, out.width = "98%", out.height="95%"}
outputdir <- "~/causalTWAS/simulations/simulation_ctwas_rss_20210416/"
runtag <- "ukb-s80.45-adi"
simutags <- paste(4, 1:5, sep = "-")
configtag <- 1

susiefs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".susieIrss.txt")
pfs <- paste0(outputdir, runtag, "_simu",simutags)
gwasfs <- paste0(pfs, ".exprgwas.txt.gz")
phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
scatter_plot_PIP_p(phenofs, susiefs, gwasfs, main ="PIP-p")
```

## Zoom view
FP example, LD with causal gene, GNPDA2

```{r sim 2, out.width = "98%", out.height="95%"}
chrom <- 4
runtag <- 4
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

FP example: LD with causal SNP, GALNT10
```{r sim 2, out.width = "98%", out.height="95%"}
runtag <- 1
chrom <- 5
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

True positive example: c1orf109
```{r sim 2, out.width = "98%", out.height="95%"}
runtag <- 4
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```
